### 2019-07-05 2-Chapters/2-Chapter/chapter25.tex
Lots of changes on Exp3, Exp4 etc notations
Lots of improvements on the arXiv papers

\abstractStartChapter{}%
%
In this chapter, we discuss the question of online algorithm selection.
%
We tackle the question of how to select a particular bandit algorithm when a practitioner is facing a particular (unknown) bandit problem.
Instead of always choosing a fixed algorithm, or running costly benchmarks before real-world deployment of the chosen algorithm, another solution could be to select a few candidate algorithms, where at least one is expected to be very efficient for the given problem, and use online algorithm selection to automatically and dynamically decide the best candidate.
We propose an extension of the Exp4 algorithm for this problem, \Aggr, and illustrate its performance on some bandit problems.

@@

\textbf{Outline.}
%
This chapter is organized as follows.
First, we give more motivations in the rest of this section, then we explain how to combine such stationary MAB algorithms and aggregate them.
We present our proposed algorithm, called \Aggr, in Section~\ref{sub:25:Aggr},
Finally, we present numerical experiments in Section~\ref{sub:25:numExp},
on Bernoulli and non-Bernoulli MAB problems,
comparing the regret of several algorithms against different aggregation algorithms.
Theoretical guarantees are shortly discussed, before we conclude in Section~\ref{sec:25:conclusion}.

>>>>

\abstractStartChapter{}%
%
In this chapter, we discuss the question of online algorithm selection.
%
We tackle the question of how to select a particular bandit algorithm when a practitioner is facing a particular (unknown) bandit problem.
Instead of always choosing a fixed algorithm, or running costly benchmarks before real-world deployment of the chosen algorithm, another solution could be to select a few candidate algorithms, where at least one is expected to be very efficient for the given problem, and use online algorithm selection to automatically and dynamically decide the best candidate.
We propose an extension of the \ExpFour{} algorithm for this problem, \Aggr, and illustrate its performance on some bandit problems.

@@

\textbf{Outline.}
%
This chapter is organized as follows.
First, we give more motivations in the rest of this section, then we explain how to combine such stationary MAB algorithms and aggregate them.
We present our proposed algorithm, called \Aggr, in Section~\ref{sub:25:Aggr},
Finally, we present numerical experiments in Section~\ref{sub:25:numExp},
on Bernoulli and non-Bernoulli MAB problems,
comparing the regret of several algorithms against different aggregation algorithms.
Theoretical guarantees are shortly discussed in Section~\ref{sec:25:theory}.
% , before we conclude in Section~\ref{sec:25:conclusion}.

### 2019-07-05 2-Chapters/3-Chapter/chapter3.tex
Lots of improvements on the arXiv papers

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=0.82\linewidth]{exampleOfRewards.pdf}
	\caption[Histogram of $10000$ \iid{} rewards obtained from three arms with a Gaussian distribution truncated to $[0,1]$, of respective means $0.1$, $0.5$ and $0.9$.]{Histogram of $10000$ \iid{} rewards obtained from three arms with a Gaussian distribution truncated to $[0,1]$, of respective means $0.1$ (in \textcolor{red}{red}), $0.5$ (in \textcolor{green}{green}) and $0.9$ (in \textcolor{blue}{blue}).}
	\label{fig:3:exampleOfRewards}
\end{figure}

>>>>

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=0.82\linewidth]{exampleOfRewards.pdf}
	\caption[Histogram of $10000$ \iid{} rewards obtained from three arms with a truncated Gaussian distribution, of respective means $0.1$, $0.5$ and $0.9$.]{Histogram of $10000$ \iid{} rewards obtained from three arms with a Gaussian distribution truncated to $[0,1]$, of respective means $0.1$ (in \textcolor{red}{red}), $0.5$ (in \textcolor{green}{green}) and $0.9$ (in \textcolor{blue}{blue}).}
	\label{fig:3:exampleOfRewards}
\end{figure}
